\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm, mathtools, bm, geometry, setspace}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage[colorlinks=true, citecolor=blue, linkcolor=blue, urlcolor=blue]{hyperref}
\geometry{margin=1in}
\onehalfspacing
\setcitestyle{authoryear, round, semicolon}

\newtheorem{assumption}{Assumption}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{corollary}{Corollary}

\title{Measuring Causal Effects under Opaque Targeting:\\
Point and Partial Identification in Overlay Experiments}
\author{Qifan Han}
\date{April 2026}

\begin{document}
\maketitle

% ============================================================
\begin{abstract}
Large digital platforms deploy proprietary targeting algorithms that allocate
advertiser treatments within randomized eligibility designs.  Realized treatment
receipt is $W_i = D_i Z_i$, where $Z_i$ is the analyst's eligibility indicator
and $D_i$ is the platform's latent targeting decision.  Standard overlay
experiments identify the Conditional Average Treatment Effect on the Treated
(CATT)---the effect for users the platform selects---but scale-up and
budget-setting decisions require the Conditional Average Treatment Effect (CATE)
for the full target population.  Because platforms optimize for response, CATT
systematically overstates CATE, and an advertiser who extrapolates the CATT to a
budget expansion will encounter predictable diminishing returns.

We make two parallel contributions addressing different information environments
within the same overlay framework.  \emph{Track A (point identification):} when
a variable that shifts the platform's delivery propensity without affecting
potential outcomes---an excluded shifter---is available, the overlay admits a
local-IV representation that point-identifies the full Marginal Treatment Effect
(MTE) schedule and, under full support, the CATE.  A distinctive feature is that
the propensity score is directly observed in the eligible arm, eliminating a
first-stage estimation step.  \emph{Track B (partial identification):} when no
excluded shifter is available---the common case for standard holdout studies---we
derive the sharp identification region $\mathrm{CATE}(x) \in [\mathrm{CITT}(x),
\mathrm{CATT}(x)]$ under monotone selection on gains and nonnegative treatment
effects; both bounds are directly computable from existing holdout data.  We
introduce the \emph{Selection Ratio} $R(x) = \mathrm{CATT}(x)/\mathrm{CATE}(x)
\in [1,\,1/e(x)]$ as a diagnostic for algorithmic cherry-picking and a decision
rule for when Track A is warranted.  We propose estimators for both tracks and
evaluate their finite-sample performance via Monte Carlo simulation calibrated to
realistic advertising settings.
\end{abstract}

% ============================================================
\section{Introduction}
\label{sec:intro}

Consider a firm running a sponsored-post campaign on Meta.  Meta's system
randomly partitions the target audience: half are placed in an exposed arm
(eligible to see the ad, $Z_i = 1$) and half in a holdout arm ($Z_i = 0$).
Within the exposed arm, Meta's auction algorithm selects which users actually
receive the ad---choosing from among the eligible those with the highest
predicted conversion probabilities given competing bids and platform objectives.
In a typical campaign, only 10--30\% of eligible users are served an ad.
Meta's standard Conversion Lift report delivers one number: the average lift in
conversions among the users the algorithm chose to expose, divided by the
exposure rate.  This is the Conditional Average Treatment Effect on the Treated
(CATT)---the lift for the algorithmically cherry-picked subpopulation.

The CATT answers the right question for one decision: \emph{Did the campaign
work for the users the platform currently targets?}  But the firm's CFO faces a
different decision: \emph{Should we double the budget next quarter?}  Doubling
the budget means the algorithm must start targeting users outside its current
selection---users with lower predicted conversion probabilities than those
currently reached.  Whether the expansion is profitable depends on the
Conditional Average Treatment Effect (CATE) across the full eligible population,
not just the CATT for the current targets.  With a treatment rate of
$e(x) = 0.10$, the CATE is a 90\%-weighted average of the effect on
currently untargeted users and the observed CATT.  The worst-case
overstatement---that is, the largest factor by which naive extrapolation of the
CATT could inflate the scale-up return---is $1/e(x) = 10$.  This worst-case
error is computable immediately from the treatment rate in any standard holdout
study.

This paper studies identification and estimation of the CATE in \emph{overlay
experiments}, where the analyst randomizes a binary eligibility indicator
$Z_i \in \{0,1\}$ while the platform's algorithm makes a latent binary targeting
decision $D_i \in \{0,1\}$.  Realized treatment receipt is
\[
  W_i = D_i Z_i,
\]
reflecting the gate structure: treatment occurs only when the analyst has made
the user eligible \emph{and} the platform has chosen to target them.  The
analyst observes $(Y_i, W_i, Z_i, X_i)$---outcomes, actual treatment,
eligibility, and pre-treatment covariates---but not the platform's targeting
rule.  This structure arises in three practically important settings.

\textbf{Programmatic advertising.}  An advertiser randomizes campaign
eligibility, but the platform's auction algorithm determines which eligible
users actually see the ad based on bids, targeting parameters, and competing
campaigns.  This is the mechanism behind Meta Conversion Lift studies, Google
Conversion Lift, and analogous holdout methodologies at major advertising
platforms.

\textbf{Within-firm simultaneous experiments.}  A firm's marketing team
activates a coupon overlay on top of the recommendation team's personalization
algorithm.  Neither team observes the other's full targeting rule; each sees
only its own randomization and realized treatment.

\textbf{Third-party measurement.}  An independent researcher or auditor
randomizes access to a platform's content---for instance, using a browser
extension that randomly enables or blocks ads for consenting participants---and
observes outcomes without knowledge of the platform's targeting rule or the
ability to direct it.

In all three cases the analyst faces one-sided noncompliance: when eligible
($Z_i = 1$), treatment receipt equals $W_i = D_i$, and the platform's selection
rule governing $D_i$ is opaque.  A key structural feature is that $D_i$ is
\emph{directly observed} in the eligible arm through $W_i = D_i$, making the
treatment rate $e(x) = P(W_i=1 \mid Z_i=1, X_i=x)$ identifiable from data.
What is opaque is not $e(x)$ but the MTE schedule for untargeted types---the
causal effect the platform's algorithm would have generated if it had targeted
users beyond its current selection.

We make two parallel contributions addressing different information environments.

\textbf{Track~A (point identification):} When a variable $S_i$ is available
that shifts the platform's delivery propensity $\pi(x,s) = P(D_i=1 \mid X_i=x,
S_i=s)$ without directly affecting users' potential outcomes---an \emph{excluded
shifter}---the overlay admits a local-IV representation in the tradition of
\citet{heckman2005structural}.  The Marginal Treatment Effect
$\mathrm{MTE}(x,u) = E[\tau_i \mid X_i=x, U_i=u]$ is identified as
$\partial_p\, E[Y_i \mid Z_i=1, X_i=x, P_i=p]$, and under full support the CATE
is recovered by integrating the MTE over $[0,1]$.  A distinctive operational
feature is that the propensity score $P_i = \pi(X_i, S_i)$ is directly observed
in the eligible arm (since $W_i = D_i$ when $Z_i = 1$), eliminating a
first-stage estimation step relative to standard IV.  Practical sources of
excluded-shifter variation include geographic differences in auction competition,
temporal fluctuations in platform load, and cross-market budget caps.

\textbf{Track~B (sharp partial identification):} When no excluded shifter is
available---the common situation for a standard holdout study---we derive the
sharp identification region for the CATE.  Under monotone selection on gains
(the platform targets users with weakly higher treatment effects) and nonnegative
treatment effects, the sharp bounds are
\[
  \mathrm{CATE}(x) \;\in\; \bigl[\,\mathrm{CITT}(x),\;\mathrm{CATT}(x)\,\bigr],
\]
where the Conditional Intent-to-Treat effect $\mathrm{CITT}(x) = E[Y\mid
Z=1,X=x] - E[Y\mid Z=0,X=x]$ and the CATT are both directly computable from
standard holdout data.  Both endpoints are attained by admissible
data-generating processes, so the bounds are sharp.  We introduce the
\emph{Selection Ratio} $R(x) := \mathrm{CATT}(x)/\mathrm{CATE}(x) \in
[1,\, 1/e(x)]$, whose observable upper bound $1/e(x)$ quantifies the worst-case
factor by which the CATT overstates scale-up returns.

The two tracks are parallel, not hierarchical.  Track~A requires additional
propensity variation but delivers a precise CATE estimate that can be plugged
directly into a budget optimization model.  Track~B is always available from
existing holdout data at zero additional cost, and serves a dual function: as a
standalone characterization of the scale-up uncertainty, and as a \emph{decision
rule} for when Track~A is warranted.  When the observable upper bound on the
Selection Ratio satisfies $1/e(x) < \bar{R}$ for a practitioner-specified
tolerance $\bar{R}$, the CATT is a sufficiently reliable proxy for the CATE and
no additional design is needed.  When $1/e(x) \geq \bar{R}$, the analyst should
seek an excluded shifter or engineer propensity variation following
\citet{waisman2025multicell}.  This sequential decision structure means Track~B
is not merely a fallback; it is the first step in any overlay analysis.

This paper connects most closely to \citet{waisman2025multicell}, who propose a
multicell experimental design in which the advertiser varies treatment propensity
by adjusting campaign budgets across cells, and show that polynomial
approximations of marginal treatment response functions recover the information
needed to solve the advertiser's budget-setting problem.  The key distinction is
experimental control: \citeauthor{waisman2025multicell} engineer propensity
variation; Track~A identifies the MTE from \emph{naturally occurring} propensity
variation within the standard overlay design, while Track~B characterizes the
limits of identification when no such variation exists.  We also complement
\citet{ye2025deep}, who study the case where a platform with a known assignment
mechanism estimates average treatment effects for $2^m$ combinations of $m$
simultaneous treatments; our paper addresses the external-experimenter case where
the assignment mechanism is unknown.

The remainder of the paper is organized as follows.  Section~\ref{sec:lit}
reviews related literature.  Section~\ref{sec:theory} develops the
identification and estimation theory, presenting the two tracks as parallel
results.  Section~\ref{sec:mc} evaluates finite-sample estimator performance via
Monte Carlo simulation.  Section~\ref{sec:conclusion} concludes.

% ============================================================
\section{Literature Review}
\label{sec:lit}

\paragraph{Marginal treatment effects and the local-IV framework.}
The marginal treatment effect framework, developed by \citet{heckman2005structural}
and building on \citet{angrist1994identification}, is the foundation for our
point-identification result.  The central idea is that when a continuously
distributed instrument shifts the probability of treatment, the causal effect
for each marginal type of complier---indexed by their latent resistance to
treatment---is identified as the derivative of the conditional outcome mean with
respect to the propensity score.  All standard treatment effect parameters,
including the ATE, ATT, and LATE, can be expressed as weighted averages of the
MTE.  \citet{vytlacil2002independence} establishes that the latent-index
structure underlying the MTE framework is equivalent to the independence and
monotonicity conditions in \citet{angrist1994identification}, so no restrictions
beyond standard IV conditions are imposed.  Empirical applications of MTE
estimation appear in, among others, \citet{carneiro2011estimating} in the
context of returns to education.  Our contribution to this literature is to show
that the overlay experiment structure provides a natural and operationally
advantageous implementation of the local-IV approach: because treatment receipt
is directly observed in the eligible arm, the platform propensity score is
identified without a separate first-stage regression.

\paragraph{Partial identification and shape restrictions.}
Our bounds are in the tradition of the partial identification literature
initiated by \citet{manski1990nonparametric}.  Manski's classic bounds rely only
on the support of observed outcomes and can be wide when outcomes are unbounded.
Our framework starts from a stronger baseline---the overlay experiment identifies
both the CITT and the CATT---and derives sharper bounds by imposing two
economically motivated shape restrictions.  The use of shape restrictions to
tighten partial identification bounds follows \citet{manski2000monotone}, who
introduce the monotone instrumental variable assumption.  In our setting, the
monotone selection assumption has a direct economic interpretation: the
platform's optimization targets high-responding users first, consistent with
profit-maximizing behavior by the platform and its advertisers.

\paragraph{Simultaneous and overlapping platform experiments.}
\citet{tang2010overlapping} and \citet{kohavi2020trustworthy} describe the
engineering infrastructure for running thousands of simultaneous A/B tests at
large technology platforms, including the orthogonal traffic assignment system
that ensures independence across experiments.  These papers address the problem
of designing simultaneous experiments from the perspective of a platform that
controls all randomizations.  \citet{ye2025deep} extend this line of work by
studying how a platform can estimate average treatment effects for all $2^m$
combinations of $m$ simultaneous treatments when only a subset of combinations
is observed, using double machine learning combined with structured neural
networks.  Their approach requires the platform's assignment mechanism to be
known.  Our paper is complementary: we address the identification problem faced
by an external experimenter who cannot observe or control the platform's
assignment rule.  The two papers approach the platform experimentation problem
from opposite sides---inside the platform versus outside it.

\paragraph{Advertising measurement and the CATT--CATE gap.}
A central empirical finding in advertising effectiveness research is that
non-experimental approaches can substantially misestimate treatment effects
relative to experimental benchmarks \citep{gordon2023close}.  This motivates
the overlay design as a preferred approach to advertising measurement when a
clean experiment is infeasible.  \citet{gordon2019comparison} provide detailed
estimates of advertising effects from large-scale field experiments at Facebook,
and their estimates inform the calibration of our Monte Carlo simulations.  The
limits of advertising measurement more broadly are discussed by
\citet{lewis2015unfavorable}, who show that advertising effects are often small
in magnitude, making precise estimation difficult even with large experiments.
Within this literature, \citet{waisman2025multicell} is the closest to our
paper.  They propose a multicell experimental design in which the advertiser
varies treatment propensity across cells by adjusting campaign budgets, and
demonstrate that this design---combined with polynomial approximations of the
MTE functions---can recover the information necessary to solve the advertiser's
optimal audience-sizing problem.  Our paper addresses the identification problem
that arises when the experimenter cannot control propensity at all: the
platform's delivery algorithm determines targeting, and the analyst can only
randomize eligibility.

\paragraph{Interference and design in platform settings.}
\citet{johari2022experimental} study identification bias in A/B tests on
two-sided platforms due to market-level interference between treated and
untreated units.  Their bias stems from SUTVA violations arising from
equilibrium effects, while our identification challenge arises from endogenous
selection by the platform's opaque targeting algorithm.  These are distinct but
complementary sources of identification failure in platform settings.  We
maintain SUTVA throughout and leave the combination of interference and opaque
targeting for future work.

% ============================================================
\section{Identification and Estimation}
\label{sec:theory}

The section proceeds as follows.  Section~\ref{subsec:setup} establishes
notation and assumptions.  Section~\ref{subsec:passive} derives a preliminary
result: the passive overlay identifies the CATT but not the CATE, making
explicit the gap that both tracks address.  Track~A
(Section~\ref{subsec:pointid}) provides point identification of the MTE and
CATE when an excluded shifter is available.  Track~B
(Section~\ref{subsec:partial}) provides sharp partial identification bounds and
the Selection Ratio diagnostic that are always available from standard holdout
data.  Section~\ref{subsec:estimation} specifies estimators for both tracks.

\subsection{Setup and Notation}
\label{subsec:setup}

Let $i$ index users in the target population.  The platform makes a latent
binary treatment decision $D_i \in \{0,1\}$, where $D_i = 1$ means the
platform's algorithm has selected user $i$ for treatment.  The analyst randomizes
a binary overlay $Z_i \in \{0,1\}$, where $Z_i = 1$ means user $i$ is eligible
to receive treatment if the platform selects them.  Realized treatment receipt is
\[
  W_i = D_i Z_i.
\]

Let $Y_i(0)$ and $Y_i(1)$ denote potential outcomes under no treatment and under
treatment, respectively, and let $\tau_i := Y_i(1) - Y_i(0)$ be the individual
treatment effect.  The observed outcome is $Y_i = Y_i(W_i)$.  The analyst
observes $(Y_i, W_i, Z_i, X_i)$, where $X_i$ is a vector of pre-treatment
covariates.

\begin{assumption}[Randomized Overlay]
\label{ass:overlay}
The overlay assignment satisfies
\[
  Z_i \;\perp\; \bigl(D_i,\; Y_i(0),\; Y_i(1)\bigr) \;\Big|\; X_i,
\]
and $0 < P(Z_i = 1 \mid X_i = x) < 1$ for all $x$ in the support of $X_i$.
\end{assumption}

Assumption~\ref{ass:overlay} requires that the analyst's eligibility
randomization is conditionally independent of the platform's targeting decision
and potential outcomes given observed covariates.  This holds by design when the
analyst randomizes $Z_i$ using a process---such as a pseudorandom hash of user
identifiers---that is independent of the platform's targeting signals.  A
potential concern is whether the platform can anticipate or react to the
analyst's randomization.  In practice, the platform's algorithm typically
operates on user features (browsing history, demographics, bid signals) rather
than on the experimenter's assignment indicator, making conditional independence
a reasonable approximation.  The overlap condition rules out degenerate designs
in which all or no users are assigned to the treatment arm.

\begin{assumption}[One-Sided Receipt]
\label{ass:onesided}
Realized treatment receipt satisfies $W_i = D_i Z_i$; in particular, $W_i = 0$
whenever $Z_i = 0$.
\end{assumption}

Assumption~\ref{ass:onesided} formalizes the gate structure of the overlay.
Users made ineligible by the analyst ($Z_i = 0$) cannot receive treatment
regardless of the platform's targeting decision.  This is appropriate for
settings in which eligibility is enforced by a technical gate---such as a
campaign audience filter or a coupon eligibility list---that the platform cannot
override.  An important implication: when $Z_i = 1$, the analyst directly
observes the platform's treatment decision through $W_i = D_i$.  This is a
distinctive feature that we exploit throughout the identification analysis.

Note that Assumption~\ref{ass:onesided} does not restrict the behavior of $D_i$
when $Z_i = 1$: within the eligible population, the platform's algorithm is free
to select any subset for treatment.  This one-sided structure is what
distinguishes the overlay from a standard IV setting with two-sided noncompliance.

% ============================================================
\subsection{Preliminary: The CATT--CATE Gap}
\label{subsec:passive}

For each $x$ in the support of $X_i$, define the following observable
quantities.  The \emph{Conditional Intent-to-Treat effect} is
\[
  \mathrm{CITT}(x) \;:=\; E[Y_i \mid Z_i=1, X_i=x] \;-\; E[Y_i \mid Z_i=0, X_i=x].
\]
The \emph{treatment rate} in the eligible arm is
\[
  e(x) \;:=\; P(W_i=1 \mid Z_i=1, X_i=x).
\]
Under Assumption~\ref{ass:onesided}, $W_i = D_i$ when $Z_i=1$, so $e(x) =
P(D_i = 1 \mid X_i = x)$: the treatment rate in the eligible arm recovers the
platform's unconditional propensity to treat users with covariates $x$.  Define
also the \emph{Conditional Average Treatment Effect on the Treated} and the
\emph{Conditional Average Treatment Effect}:
\[
  \mathrm{CATT}(x) \;:=\; E[\tau_i \mid D_i=1,\, X_i=x], \qquad
  \mathrm{CATE}(x) \;:=\; E[\tau_i \mid X_i=x].
\]

\begin{proposition}[Passive Overlay Identifies the CATT]
\label{prop:att}
Suppose Assumptions~\ref{ass:overlay} and~\ref{ass:onesided} hold.  Then, for
every $x$ with $e(x) > 0$,
\begin{equation}
  \mathrm{CITT}(x) \;=\; E[D_i\,\tau_i \mid X_i=x],
  \label{eq:itt}
\end{equation}
and
\begin{equation}
  \frac{\mathrm{CITT}(x)}{e(x)} \;=\; \mathrm{CATT}(x).
  \label{eq:catt}
\end{equation}
Hence the passive overlay point-identifies $\mathrm{CATT}(x)$ but not
$\mathrm{CATE}(x)$ in general.
\end{proposition}

Proposition~\ref{prop:att} is the foundational identification result for the
overlay experiment.  The ratio $\mathrm{CITT}(x)/e(x)$ is the Wald estimator
applied within the overlay design, and it identifies the average treatment effect
for the platform's selected subpopulation.  The proof follows from the
conditional independence of $Z_i$ (Assumption~\ref{ass:overlay}) and the gate
structure of $W_i$ (Assumption~\ref{ass:onesided}); details are in the
Appendix.

The managerial interpretation is immediate and important.  An advertiser who
runs a passive overlay and computes $\mathrm{CITT}(x)/e(x)$ obtains a valid
estimate of the campaign's effectiveness \emph{for the users the platform
currently targets}.  This is the correct object for evaluating whether the
campaign has positive returns under the current targeting strategy, and for
holding the platform accountable for delivering the promised audience.  However,
the CATT is the wrong input for scale-up decisions.  A decision to expand the
campaign---increasing the audience size, the budget, or the geographic
footprint---implicitly asks what the campaign effect would be on users the
platform does not currently target.  Those users are drawn from the part of the
population for which the platform's algorithm predicts lower response, so the
CATE is generically below the CATT.

Formally, the gap arises from the decomposition
\[
  \mathrm{CATE}(x) \;=\; e(x)\,\mathrm{CATT}(x) \;+\; (1-e(x))\,\mathrm{CATU}(x),
\]
where $\mathrm{CATU}(x) := E[\tau_i \mid D_i=0, X_i=x]$ is the conditional
average effect on the untreated.  If the platform selects users with
above-average treatment response---which is the platform's optimization
objective---then $\mathrm{CATT}(x) \geq \mathrm{CATE}(x) \geq \mathrm{CATU}(x)$.
The passive overlay cannot identify the CATE because the untreated
region ($Z_i=1, D_i=0$) reveals only the composite $E[Y_i(0) \mid X_i=x]$
and not the counterfactual $E[Y_i(1) \mid D_i=0, X_i=x]$.  The following two
sections present parallel solutions.  Track~A (Section~\ref{subsec:pointid})
achieves point identification when an excluded shifter generates within-cell
variation in the platform's propensity.  Track~B (Section~\ref{subsec:partial})
characterizes the sharp identified set using only the observable treatment rate
and the ITT, without any additional experimental variation.

\begin{remark}
  The CATT characterization in Proposition~\ref{prop:att} is a preliminary
  result that underlies both tracks, not a contribution in its own right.  It
  is the Wald estimator applied to one-sided noncompliance, and is included to
  make the paper self-contained and to fix notation for the CATT--CATE gap
  that motivates the analysis.
\end{remark}

% ============================================================
\subsection{Track A: Point Identification via an Excluded Shifter}
\label{subsec:pointid}

We now consider point identification when an excluded shifter is available.

\textbf{Propensity scores in this section.}  Two propensity scores appear.  The
marginal propensity $e(x) = P(D_i=1 \mid X_i=x)$ was identified from the
passive overlay (Section~\ref{subsec:passive}) and is constant within a
covariate cell $x$.  Because $e(x)$ does not vary within $x$, the
derivative-based local-IV argument is unavailable in the passive setting.
Track~A introduces an excluded shifter $S_i$ to generate within-cell variation
in the \emph{conditional propensity} $\pi(x,s) = P(D_i=1 \mid X_i=x, S_i=s)$.
For a given covariate cell $x$, different values of $s$ produce different
delivery rates, enabling identification of the MTE as a derivative.

Let $S_i$ denote an observed variable that shifts the platform's delivery
propensity without directly affecting users' potential outcomes conditional on
$X_i$.  Intuitively, $S_i$ represents variation in how aggressively the
platform targets eligible users that is unrelated to the users' response to
treatment.

In practice, several sources of such variation arise naturally in advertising
contexts.  \emph{Geographic variation in auction competition}: the platform's
cost of delivering an ad varies across markets due to differences in competing
advertiser bids.  A lower auction price in a market increases the platform's
propensity to deliver to eligible users in that market, without directly
affecting how those users respond to the ad.  \emph{Temporal variation in
platform load}: the platform's ad delivery algorithm adjusts aggressively based
on available impression inventory, which fluctuates with time of day and day of
week in ways that shift delivery propensity without directly affecting purchase
intent.  \emph{Cross-market budget allocation}: when an advertiser runs the
overlay campaign across markets with different per-market budget caps, effective
per-user budgets vary across markets in a way that shifts delivery propensity
while campaign content remains unchanged.  This last source is the closest
analog to the multicell design of \citet{waisman2025multicell}, with the
critical difference that in our setting the budget variation is incidental rather
than designed.

\begin{assumption}[Excluded Shifter and Latent Index]
\label{ass:excluded}
There exists a scalar latent variable $U_i$ and a measurable function $\pi(\cdot,\cdot)$
such that:
\begin{enumerate}
  \item The platform assignment rule is $D_i = \mathbf{1}\{\pi(X_i, S_i) \geq U_i\}$.
  \item Conditional on $X_i = x$, the latent type satisfies $U_i \sim
    \mathrm{Uniform}[0,1]$.
  \item $(Y_i(0),\, Y_i(1),\, U_i) \perp S_i \mid X_i$ \emph{(exclusion restriction)}.
  \item For each $x$, the support of $\pi(x, S_i) \mid X_i=x$ contains an open
    interval.
  \item $Z_i \perp (Y_i(0),\, Y_i(1),\, D_i,\, U_i) \mid (X_i, S_i)$.
\end{enumerate}
\end{assumption}

Condition 1 specifies a latent-index model for the platform's targeting rule:
user $i$ is targeted if the platform's predicted value of targeting them,
$\pi(X_i, S_i)$, exceeds a user-specific resistance threshold $U_i$.
\citet{vytlacil2002independence} establishes that this structure is equivalent
to the independence and monotonicity conditions of \citet{angrist1994identification},
so no restriction beyond standard IV conditions is imposed.

Condition 2 is a normalization.  Under it, $\pi(x,s) = P(D_i=1 \mid X_i=x,
S_i=s)$ is the platform's propensity score conditional on the shifter.  We
define $P_i := \pi(X_i, S_i)$ as the individual-level propensity.  Note the
distinction from $e(x) = P(D_i=1 \mid X_i=x)$: the former conditions on the
shifter and varies within a covariate cell; the latter is the marginal propensity
observable in the passive overlay.

Condition 3 is the exclusion restriction.  In the geographic competition
example, it requires that auction prices affect the platform's delivery
decision but not the causal effect of seeing an ad on purchase probability,
conditional on the user's demographic and behavioral covariates.  This condition
is standard in IV analysis and is the analog of the exogeneity assumption
maintained in \citet{waisman2025multicell}.

Condition 4 ensures sufficient variation in the propensity score, enabling
identification of the MTE at a continuum of propensity values.  Condition 5
extends the randomization condition to allow the analyst to condition on $S_i$.

Define the outcome regressions in the eligible and ineligible arms:
\[
  \mu_1(x,p) \;:=\; E[Y_i \mid Z_i=1,\, X_i=x,\, P_i=p], \qquad
  \mu_0(x) \;:=\; E[Y_i \mid Z_i=0,\, X_i=x].
\]
Define the Marginal Treatment Effect:
\[
  \mathrm{MTE}(x,u) \;:=\; E[\tau_i \mid X_i=x,\, U_i=u].
\]
This is the average treatment effect for users with covariate value $x$ whose
latent resistance to treatment is exactly $u$.

\begin{proposition}[Outcome Representation]
\label{prop:representation}
Suppose Assumptions~\ref{ass:overlay},~\ref{ass:onesided}, and~\ref{ass:excluded}
hold.  Then, for every $(x,p)$ in the support of $(X_i, P_i)$,
\begin{equation}
  \mu_1(x,p) \;=\; \mu_0(x) \;+\; \int_0^p \mathrm{MTE}(x,u)\,du.
  \label{eq:representation}
\end{equation}
\end{proposition}

Proposition~\ref{prop:representation} is a key representation result.  It shows
that the difference in conditional outcome means between eligible and ineligible
arms, $\mu_1(x,p) - \mu_0(x)$, aggregates the MTE from the most-responsive type
($u=0$) up to the current propensity level $p$.  Users treated when $P_i = p$
are those with $U_i \leq p$---the users with sufficiently low resistance to
targeting---and their average treatment effect is the integral of the MTE over
$[0,p]$.  This is the local-IV representation from \citet{heckman2005structural},
with our excluded shifter playing the role of the instrument.

An important operational feature of the overlay design is that the platform
propensity $P_i = \pi(X_i, S_i)$ is directly observed in the eligible arm
(since $W_i = D_i$ when $Z_i=1$), without requiring a separate first-stage
regression on the instrument.  This gives the overlay a practical advantage over
a standard IV setup, and is the analog of the direct budget-to-propensity
correspondence in the multicell design of \citet{waisman2025multicell}.

\begin{theorem}[Point Identification of the MTE and the CATE]
\label{thm:pointid}
Suppose Assumptions~\ref{ass:overlay},~\ref{ass:onesided}, and~\ref{ass:excluded}
hold, and suppose $p \mapsto \mu_1(x,p)$ is differentiable on the interior of
the support of $P_i \mid X_i=x$.  Then:
\begin{enumerate}
  \item For every $(x,p)$ in the interior of the support of $(X_i, P_i)$,
  \[
    \mathrm{MTE}(x,p) \;=\; \frac{\partial}{\partial p}\,\mu_1(x,p).
  \]
  \item If the support of $P_i \mid X_i=x$ is $[0,1]$ for each $x$, then
  \[
    \mathrm{CATE}(x) \;=\; \int_0^1 \mathrm{MTE}(x,u)\,du.
  \]
  \item Integrating over $X_i$, the population average treatment effect is
  \[
    \mathrm{ATE} \;:=\; E[\tau_i] \;=\; E\!\left[\int_0^1 \mathrm{MTE}(X_i,u)\,du\right].
  \]
\end{enumerate}
\end{theorem}

Theorem~\ref{thm:pointid} establishes that, under the excluded shifter, the
overlay experiment point-identifies the full MTE schedule as the derivative of
an observable conditional expectation.  The logic follows directly from
Proposition~\ref{prop:representation}: differentiating both sides of
\eqref{eq:representation} with respect to $p$ recovers the MTE at each
propensity level.

The relationship to the \citet{heckman2005structural} framework is direct and by
construction.  What is distinctive about the overlay design is the operational
clarity with which propensity score variation is generated.  In a standard IV
setting, propensity variation arises from the instrument shifting the selection
equation, and the propensity must be estimated from the joint distribution of the
instrument and treatment.  In the overlay, the eligible arm directly reveals
who was treated at each level of the shifter, so $P_i$ is observable rather than
latent.  The MTE can then be estimated by standard nonparametric derivative
methods applied to $\mu_1(x,p)$.

The full-support condition in part 2 of Theorem~\ref{thm:pointid} is
substantive: it requires that the excluded shifter generate propensity variation
spanning the full range $[0,1]$.  In practice, the support may be limited---
geographic or temporal variation may shift the propensity only within a
subrange.  In such cases, Theorem~\ref{thm:pointid} identifies the MTE on the
observed support, and one can combine the identified MTE segment with the shape
restrictions of Section~\ref{subsec:partial} to bound the CATE.  This hybrid
approach is analogous to the ``extrapolation'' exercises in the MTE literature
\citep{carneiro2011estimating} and directly mirrors the approach of
\citeauthor{waisman2025multicell}, who discuss how to extrapolate polynomial MTE
approximations beyond the observed propensity support.

% ============================================================
\subsection{Track B: Sharp Partial Identification Bounds}
\label{subsec:partial}

We now return to the passive setting in which no excluded shifter is available.
The treatment rate $e(x) = P(D_i=1 \mid X_i=x)$ is identified from the eligible
arm, but because $e(x)$ is a deterministic function of $X_i$, there is no
within-covariate-cell variation in the platform's propensity.  The
derivative-based local-IV argument is therefore unavailable.  We instead impose
a latent-index model and derive sharp bounds under two economically motivated
restrictions on the MTE schedule.

\begin{assumption}[Passive Latent Index]
\label{ass:passive}
There exists a scalar latent variable $U_i$ such that $D_i = \mathbf{1}\{e(X_i)
\geq U_i\}$, with $U_i \mid X_i = x \sim \mathrm{Uniform}[0,1]$.
\end{assumption}

Assumption~\ref{ass:passive} is a latent-index representation of the platform's
targeting rule in the absence of an excluded shifter.  Under this structure,
users with the lowest values of $U_i$---the highest intrinsic propensity to be
targeted---are selected first as the platform's budget or delivery intensity
increases.  This is consistent with a platform that ranks users by predicted
response and targets the top-$e(x)$ fraction within each covariate cell.

\begin{assumption}[Monotone Selection on Gains]
\label{ass:monotone}
For every $x$, the MTE schedule $u \mapsto \mathrm{MTE}(x,u)$ is weakly
decreasing on $[0,1]$.
\end{assumption}

Assumption~\ref{ass:monotone} is the key behavioral restriction.  It states that
users with lower latent resistance to being targeted ($U_i$ closer to zero) have
weakly higher treatment effects---the platform's selection criterion is
positively correlated with treatment response.  This is precisely what a
profit-maximizing advertising platform is designed to achieve: the targeting
algorithm predicts response rates and allocates impressions to high-predicted-
response users.

The economic basis for this assumption is strong.  Advertising platforms sell
campaign performance (conversions, clicks, purchases) and are therefore
incentivized to direct ads toward users most likely to respond.  An advertiser
paying on a cost-per-click or cost-per-conversion basis creates direct pressure
for the platform to select high-responders.  Empirical evidence from large-scale
advertising experiments is consistent with substantial positive selection on gains
\citep{gordon2019comparison, waisman2025multicell}: the users the platform
chooses to target within an eligible audience exhibit significantly higher
response rates than the eligible audience as a whole.

We emphasize that Assumption~\ref{ass:monotone} does not require perfect
targeting.  It requires only that selection be positively correlated with
treatment response on average---a far weaker condition that accommodates
prediction errors and multi-objective optimization (e.g., targeting users with
high brand affinity in addition to high purchase likelihood).

\begin{assumption}[Nonnegative Treatment Effects]
\label{ass:nonneg}
$\mathrm{MTE}(x,u) \geq 0$ for all $(x,u)$.
\end{assumption}

Assumption~\ref{ass:nonneg} rules out harmful treatment effects.  In advertising
contexts, the primary concern is whether exposure to an ad causes users to
purchase a product they would not otherwise have bought; the possibility that
exposure causes negative outcomes (e.g., brand backlash or substitution toward
competing products) is an exception rather than the rule.  Critically,
Assumption~\ref{ass:nonneg} is used only to establish the lower bound: the upper
bound in Theorem~\ref{thm:sharp} holds under Assumption~\ref{ass:monotone}
alone.  Our Monte Carlo analysis in Section~\ref{sec:mc} explicitly examines
what happens to the bounds when nonnegative effects is violated, providing a
robustness check on this assumption.

\begin{lemma}[MTE Representation under Passive Overlay]
\label{lem:overlay}
Suppose Assumptions~\ref{ass:overlay},~\ref{ass:onesided}, and~\ref{ass:passive}
hold.  Then, for every $x$,
\begin{equation}
  \mathrm{CITT}(x) \;=\; \int_0^{e(x)} \mathrm{MTE}(x,u)\,du,
  \label{eq:citt_rep}
\end{equation}
\begin{equation}
  \mathrm{CATE}(x) \;=\; \int_0^1 \mathrm{MTE}(x,u)\,du.
  \label{eq:cate_rep}
\end{equation}
\end{lemma}

Lemma~\ref{lem:overlay} is a technical bridge between the observable reduced
form and the latent MTE schedule.  The CITT integrates the MTE over the treated
region $[0, e(x)]$---users the platform selects---while the CATE integrates the
MTE over the full support $[0,1]$.  The difference, $\mathrm{CATE}(x) -
\mathrm{CITT}(x) = \int_{e(x)}^1 \mathrm{MTE}(x,u)\,du$, is the contribution
of the untreated region, which is unobserved but bounded under
Assumptions~\ref{ass:monotone} and~\ref{ass:nonneg}.

\begin{theorem}[Sharp Identification Region]
\label{thm:sharp}
Fix $x$ with $e(x) \in (0,1)$ and $\mathrm{CITT}(x) \geq 0$.  Suppose
Assumptions~\ref{ass:overlay},~\ref{ass:onesided},~\ref{ass:passive},~\ref{ass:monotone},
and~\ref{ass:nonneg} hold.  Then
\begin{equation}
  \mathrm{CATE}(x) \;\in\; \bigl[\,\mathrm{CITT}(x),\;\mathrm{CATT}(x)\,\bigr].
  \label{eq:bounds}
\end{equation}
The bounds are sharp: both endpoints are attained by admissible
data-generating processes consistent with the observable statistics
$(e(x),\, \mathrm{CITT}(x))$.
\end{theorem}

The identification region in Theorem~\ref{thm:sharp} has an intuitive structure.
The lower bound $\mathrm{CITT}(x)$ arises from the worst case in which treatment
effects are zero for all untreated types ($U_i > e(x)$): the CATE equals the
CITT because the campaign has no value for the users the platform does not
target.  The upper bound $\mathrm{CATT}(x)$ arises from the best case in which
the MTE is constant across all types: the platform's selection adds no additional
efficiency beyond random selection, so the CATE equals the CATT.

Both bounds are identified directly from experimental data: the CITT from the
overlay design and the CATT from Proposition~\ref{prop:att}.  This makes the
bounds immediately implementable without any additional experimental variation.

The width of the identified set, $\mathrm{CATT}(x) - \mathrm{CITT}(x) =
\mathrm{CATT}(x)\cdot(1-e(x))$, is informative.  When $e(x)$ is close to one
the bounds are narrow and the CATE is close to the CATT---the platform treats
nearly all eligible users, suggesting the campaign's eligible audience is already
highly selective.  When $e(x)$ is small the bounds are wide, reflecting
substantial uncertainty about treatment effects for the marginal user.  This
connects directly to the practitioner's question: a narrow identified set
justifies treating the CATT as a reliable proxy for scale-up returns, while a
wide identified set signals the need for additional experimental variation.

\begin{remark}
The upper bound $\mathrm{CATE}(x) \leq \mathrm{CATT}(x)$ holds under
Assumption~\ref{ass:monotone} alone (without nonnegative effects).  The lower bound
$\mathrm{CATE}(x) \geq \mathrm{CITT}(x)$ additionally requires
Assumption~\ref{ass:nonneg}.  When nonnegative effects is violated---as can arise in
practice when some users have negative responses to advertising---the true CATE
may fall below the CITT, and only the upper bound remains valid.
\end{remark}

\subsubsection{The Selection Ratio and a Decision Rule}

Theorem~\ref{thm:sharp} motivates a natural summary diagnostic for the degree of
algorithmic cherry-picking.

\begin{definition}[Selection Ratio]
The \emph{Selection Ratio} at covariate value $x$ is
\begin{equation}
  R(x) \;:=\; \frac{\mathrm{CATT}(x)}{\mathrm{CATE}(x)}.
  \label{eq:sr}
\end{equation}
\end{definition}

The Selection Ratio measures how much the platform's targeted subpopulation
outperforms the full population on average.  If the platform assigns treatment
uniformly at random, $R(x) = 1$ and CATT = CATE.  If the algorithm perfectly
targets the highest-responding users, $R(x)$ can be substantially above one,
indicating that the campaign's observed lift significantly overstates its
population-level effect.

\begin{corollary}[Partial Identification of the Selection Ratio]
\label{cor:ratio}
Under the conditions of Theorem~\ref{thm:sharp},
\begin{equation}
  R(x) \;\in\; \left[1,\;\frac{1}{e(x)}\right].
  \label{eq:ratio_bounds}
\end{equation}
\end{corollary}

The lower bound $R(x) \geq 1$ follows from monotone selection (CATT $\geq$
CATE).  The upper bound $R(x) \leq 1/e(x)$ follows because CATE $\geq$ CITT $=
e(x)\cdot$CATT.  A lower treatment rate $e(x)$ implies higher potential for
cherry-picking, because the platform must be highly selective to reach its
treatment rate target.  In the extreme case of a very targeted campaign with
$e(x) = 0.1$, the Selection Ratio could be as large as 10, meaning the observed
CATT could overstate the population CATE by a factor of up to 10.

Practically, the upper bound on $R(x)$ is directly computable from the treatment
rate $e(x)$, which is observed in any overlay experiment.  This yields a
concrete decision rule linking Track~B to Track~A.

\begin{remark}[Decision Rule]
\label{rem:decision}
Let $\bar{R} > 1$ be a practitioner-specified tolerance for the worst-case
scale-up overstatement.  If $1/e(x) < \bar{R}$, the CATT is a sufficiently
reliable proxy for the CATE under the maintained assumptions, and no additional
experimental variation is needed.  If $1/e(x) \geq \bar{R}$, the analyst should
seek an excluded shifter (Track~A) or engineer propensity variation following
\citet{waisman2025multicell} before using the CATT to inform scale-up decisions.
In either case, the Track~B analysis---which costs nothing beyond the existing
holdout study---is the natural first step in any overlay measurement exercise.
\end{remark}

% ============================================================
\subsection{Estimation}
\label{subsec:estimation}

The identification results of Sections~\ref{subsec:pointid}
and~\ref{subsec:partial} suggest natural estimators.  We specify these here;
Section~\ref{sec:mc} evaluates their finite-sample performance.

\subsubsection{Track B: Plug-in Estimators and Imbens--Manski Inference}

The sharp bounds $[\mathrm{CITT}(x), \mathrm{CATT}(x)]$ and the Selection Ratio
upper bound $1/e(x)$ are smooth functionals of the joint distribution of
$(Y_i, W_i, Z_i, X_i)$, admitting plug-in estimators.  Let flexible regression
(e.g., local polynomial, series, or cross-fitted ML) produce estimates
$\hat{m}_d(x) = \hat{E}[Y_i \mid Z_i=d, X_i=x]$ and $\hat{e}(x) =
\hat{P}(W_i=1 \mid Z_i=1, X_i=x)$.  Define
\begin{align}
  \hat{L}(x) &= \hat{\mathrm{CITT}}(x) \;=\; \hat{m}_1(x) - \hat{m}_0(x), \\
  \hat{U}(x) &= \hat{\mathrm{CATT}}(x) \;=\; \hat{L}(x)\,/\,\hat{e}(x).
\end{align}

\textbf{Inference on the true CATE.}  To construct a confidence interval that
covers the true (scalar) $\mathrm{CATE}(x)$ with probability $\geq 1-\alpha$,
we apply \citet{imbens2004confidence} as refined by \citet{stoye2009more}.
The Stoye (2009) interval has pointwise asymptotic validity: it covers
$\mathrm{CATE}(x)$ with probability approaching $1-\alpha$ for each fixed $x$.
Uniform validity over $x$ requires additional conditions and is left for future
work.
Let $\hat{\sigma}_L^2$ and $\hat{\sigma}_U^2$ be asymptotic variance estimates
for $\hat{L}(x)$ and $\hat{U}(x)$.  Solve for the critical value $\hat{c}_n$
satisfying
\[
  \Phi\!\left(\hat{c}_n + \frac{\sqrt{n}\bigl(\hat{U}(x) -
  \hat{L}(x)\bigr)}{\max(\hat{\sigma}_L,\hat{\sigma}_U)}\right) -
  \Phi(-\hat{c}_n) \;=\; 1-\alpha,
\]
yielding the confidence interval
\[
  \widehat{\mathrm{CI}}_{1-\alpha}(x) \;=\; \Bigl[\hat{L}(x) -
  \hat{c}_n\,\hat{\sigma}_L/\sqrt{n},\;\;
  \hat{U}(x) + \hat{c}_n\,\hat{\sigma}_U/\sqrt{n}\Bigr].
\]
The variance $\hat{\sigma}_U^2$ for the ratio estimator is computed via the
delta method.  Because $\hat{L}(x)$ and $\hat{e}(x)$ both depend on the
$Z_i = 1$ subsample, they are correlated; ignoring this covariance overstates
$\hat{\sigma}_U^2$ and produces conservative inference:
\begin{equation}
  \hat{\sigma}_U^2 \;\approx\; \frac{\hat{\sigma}_{\mathrm{CITT}}^2}{\hat{e}^2}
  + \frac{\hat{\mathrm{CATT}}^2\,\hat{\sigma}_e^2}{\hat{e}^2}
  - \frac{2\,\hat{\mathrm{CATT}}}{\hat{e}^3}\,
    \widehat{\mathrm{Cov}}\!\bigl(\hat{L}(x),\,\hat{e}(x)\bigr),
  \label{eq:delta_var}
\end{equation}
where $\widehat{\mathrm{Cov}}(\hat{L},\hat{e}) =
n_1(x)^{-1}\widehat{\mathrm{Cov}}(Y_i, W_i \mid Z_i=1, X_i=x)$ and $n_1(x)$
is the effective sample size in the eligible arm at $x$.  In practice,
$\widehat{\mathrm{Cov}}(Y_i, W_i \mid Z_i=1, X_i=x)$ is estimated as the
sample covariance of $Y_i$ and $W_i$ among observations with $Z_i=1$ in a
neighborhood of $x$ (using the same kernel or series weights as the outcome
regressions $\hat{m}_d(x)$).

\textbf{Selection Ratio.}  A one-sided $(1-\alpha)$ confidence upper bound on
$R(x)$ via the delta method is
\[
  \hat{R}^{\max}_{1-\alpha}(x) \;=\; \frac{1}{\hat{e}(x)} +
  z_{1-\alpha}\cdot\frac{\hat{\sigma}_e}{\hat{e}(x)^2\sqrt{n_1(x)}}.
\]

\subsubsection{Track A: Finite-Differences MTE Estimator}

When the excluded shifter $S_i$ takes $C$ discrete values with propensity
scores $0 < p_1 < \cdots < p_C < 1$, Theorem~\ref{thm:pointid} identifies the
MTE through the derivative of $\mu_1(x,p)$.  With discrete support, estimate
the conditional outcome mean $\hat{\mu}_1(x, p_c) = \hat{E}[Y_i \mid Z_i=1,
X_i=x, \hat{P}_i = p_c]$ by local regression within each shifter cell, and
approximate the derivative by finite differences at midpoints
$\bar{p}_c = (p_c + p_{c+1})/2$:
\begin{equation}
  \hat{\mathrm{MTE}}(x, \bar{p}_c) \;=\; \frac{\hat{\mu}_1(x, p_{c+1}) -
  \hat{\mu}_1(x, p_c)}{p_{c+1} - p_c}, \qquad c = 1, \ldots, C-1.
  \label{eq:mte_fd}
\end{equation}
Integrate to estimate the CATE:
\begin{equation}
  \hat{\mathrm{CATE}}(x) \;=\; \underbrace{\sum_{c=1}^{C-1}
    \hat{\mathrm{MTE}}(x,\bar{p}_c)(p_{c+1}-p_c)}_{\text{identified on }
    [p_1,p_C]}
  \;+\; \underbrace{\hat{\mathrm{MTE}}(x,\bar{p}_1)\cdot p_1 +
    \hat{\mathrm{MTE}}(x,\bar{p}_{C-1})\cdot(1-p_C)}_{\text{linear
    extrapolation on }[0,p_1]\cup[p_C,1]}.
  \label{eq:cate_fd}
\end{equation}
Standard errors are obtained by propagating uncertainty through
\eqref{eq:mte_fd}--\eqref{eq:cate_fd} via the delta method, or by pairs
bootstrap within each shifter cell.

\begin{remark}
When $S_i$ is continuously distributed, $\hat{\mathrm{MTE}}(x,p) =
\hat{\partial}_p\,\mu_1(x,p)$ is estimated by local polynomial derivative
methods \citep{fan1996local} with bandwidth selected by cross-validation.  The
asymptotic theory is standard; we leave bandwidth selection for future work and
focus the Monte Carlo analysis on the practically common discrete-shifter case.
\end{remark}

% ============================================================
\section{Monte Carlo Simulation}
\label{sec:mc}

We assess the finite-sample performance of the estimators specified in
Section~\ref{subsec:estimation} via Monte Carlo simulation.  Our primary goals
are: (i) to evaluate coverage and width of the Imbens--Manski confidence interval
(Track~B) as a function of sample size, treatment rate $\bar{e}$, and the
complexity of the platform's assignment rule; (ii) to assess the finite-differences
MTE estimator and CATE reconstructor (Track~A) in terms of bias and RMSE as $n$
grows; and (iii) to stress-test both tracks when the maintained assumptions are
violated.  All results are based on 1,000 simulation replications.

\subsection{Data Generating Processes}
\label{subsec:dgp}

We design three main DGPs that share the same treatment-effect schedule but vary
the complexity of the platform's assignment rule, and two robustness DGPs that
modify the treatment-effect schedule to violate the maintained assumptions.  This
design isolates the role of assignment-rule complexity in the main results and
tests assumption sensitivity in the robustness checks.

\paragraph{Common outcome model.} For all DGPs, individual potential outcomes are
\begin{equation}
  Y_i(d) \;=\; d\cdot\tau(U_i) \;+\; \varepsilon_i, \qquad
  \varepsilon_i \;\sim\; N(0,1),
  \label{eq:dgp_outcome}
\end{equation}
where $\tau(U_i)$ is the individual treatment effect determined by the latent
type $U_i \sim \mathrm{Uniform}[0,1]$, which is independent of $X_i$ and
$\varepsilon_i$.  The platform's targeting follows the latent-index model
$D_i = \mathbf{1}\{U_i \leq e_i\}$, where $e_i$ is the delivery propensity
for unit $i$.  The analyst assigns eligibility $Z_i \sim \mathrm{Bernoulli}(0.5)$
independently.

\paragraph{Common MTE schedule (DGPs 1--3).}
All three main DGPs use the same linearly decreasing MTE:
\[
  \tau(u) \;=\; 2(1 - u),
\]
which yields $\mathrm{CATE} = \int_0^1 2(1-u)\,du = 1.00$.  Because users with
lower $U_i$ respond more strongly \emph{and} are the ones the platform targets
(lower $U_i$ means lower cost of delivery in the latent-index model), the
platform's selection on $U_i$ creates positive selection on gains:
$\mathrm{CATT} > \mathrm{CATE}$ under all three DGPs.  The three DGPs differ
only in how the propensity $e_i$ depends on covariates.

\paragraph{DGP 1 (Constant quota).}
The platform uses a uniform quota: $e_i = 0.30$ for all units.  This is the
simplest assignment rule---a fixed-rate targeting algorithm without covariate
targeting.  True estimands: $\mathrm{CATE} = 1.00$, $\mathrm{CATT} = 1.70$,
$\mathrm{CITT} = 0.51$, $\mathrm{SR} = 1.70$, $\mathrm{SR}_{ub} = 3.33$.

\paragraph{DGP 2 (Logistic score).}
The propensity is a logistic function of observed covariate $X_i \sim N(0,1)$:
\[
  e_i \;=\; \sigma(\alpha + 2\,X_i), \qquad \sigma(t) = (1+e^{-t})^{-1},
\]
where $\alpha$ is calibrated so that $\bar{e} = \mathbb{E}[e_i] = 0.30$
(yielding $\alpha = -1.38$).  This represents a realistic covariate-based
targeting rule of the form used in standard logistic propensity models.  True
estimands: $\mathrm{CATE} = 1.00$, $\mathrm{CATT} = 1.44$, $\mathrm{CITT} =
0.43$, $\mathrm{SR} = 1.44$, $\mathrm{SR}_{ub} = 3.33$.

\paragraph{DGP 3 (Nonlinear ML score).}
The propensity involves nonlinear interactions:
\[
  e_i \;=\; \sigma\!\left(\gamma_0 + 2X_{i1}^2 + X_{i2} - 2X_{i1}X_{i2}\right),
\]
where $X_{i1}, X_{i2} \sim N(0,1)$ and $\gamma_0$ is calibrated to
$\bar{e} = 0.30$ (yielding $\gamma_0 = -2.98$).  This represents a modern
machine-learning targeting algorithm with nonlinear feature interactions.  True
estimands: $\mathrm{CATE} = 1.00$, $\mathrm{CATT} = 1.31$, $\mathrm{CITT} =
0.39$, $\mathrm{SR} = 1.31$, $\mathrm{SR}_{ub} = 3.33$.

The progression DGP 1 $\to$ DGP 2 $\to$ DGP 3 reflects increasing algorithmic
complexity.  The true SR decreases from 1.70 to 1.44 to 1.31, which reflects
the fact that the nonlinear ML algorithm, by targeting on $X_i$ rather than
directly on $U_i$, achieves somewhat less selection on gains.  Importantly, the
SR upper bound $1/\bar{e} = 3.33$ is the same across all three DGPs, illustrating
that the observable treatment rate correctly bounds the SR regardless of the
assignment rule's complexity.

\paragraph{DGP-R1 (Hump-shaped MTE, monotone selection violated).}
Using DGP~1 assignment but replacing the MTE with
$\tau(u) = 8u(1-u)$,
which peaks at $u = 0.50$.  Now $\tau(0) = 0$ and $\tau(0.30) > \tau(1.00)$,
so the platform preferentially targets users with low response (near $u=0$).
This violates Assumption~\ref{ass:monotone}: the platform selects against gains.
True estimands: $\mathrm{CATE} = 1.33 > \mathrm{CATT} = 0.96$, so the upper
bound $\mathrm{CATT}$ lies \emph{below} the true CATE.

\paragraph{DGP-R2 (Negative-tail MTE, nonnegative effects violated).}
Using DGP~1 assignment with $\tau(u) = 2 - 4u$,
which is positive for $u < 0.50$ and negative for $u > 0.50$.
True estimands: $\mathrm{CATE} \approx 0 < \mathrm{CITT} = 0.42$, so the lower
bound $\mathrm{CITT}$ lies strictly \emph{above} the true CATE.

\paragraph{Track~A excluded-shifter design.}
For the point-identification exercise we augment DGP~1 with a geographic
excluded shifter $S_i \in \{0,1,2\}$ representing three market types with
propensities $\pi_s \in \{0.20, 0.35, 0.55\}$.  The outcome is generated
as in~\eqref{eq:dgp_outcome} with $\tau(u) = 2(1-u)$, so the true MTE at
the observed midpoints is $\mathrm{MTE}(0.275) = 1.45$ and
$\mathrm{MTE}(0.450) = 1.10$, and $\mathrm{CATE} = 1.00$.  We estimate
MTE by finite differences across markets and reconstruct the CATE by
integrating via linear extrapolation beyond the observed propensity support
$[0.20,\,0.55]$.

\subsection{Results}
\label{subsec:sim_results}

\paragraph{Track B: partial identification across DGPs (Table~\ref{tab:trackb}).}

Table~\ref{tab:trackb} reports the bias and RMSE of the CATT estimator and the
coverage and average width of the 90\% Imbens--Manski CI for the CATE across
sample sizes $n \in \{500,\,2{,}000,\,10{,}000,\,50{,}000\}$ and DGPs 1--3.

Three findings stand out.  First, the CATT estimator is virtually unbiased at
all sample sizes across all three DGPs: the largest absolute bias is $0.015$
(DGP~1, $n=500$), and it shrinks toward zero as $n$ grows.  Second, the
Imbens--Manski CI achieves the nominal 90\% coverage at moderate to large sample
sizes.  Coverage dips below 90\% only at $n=500$ under DGP~2 ($0.930$) and
DGP~3 ($0.846$), where the nonlinear assignment rule concentrates the propensity
mass away from 0.50, increasing estimation variance.  By $n = 2{,}000$ coverage
is above 99.7\% across all DGPs, and by $n = 10{,}000$ it is 100\%.  Third,
the CI width narrows as the assignment rule better targets the high-response
users: DGP~1 (constant quota, $\mathrm{SR} = 1.70$) has the widest interval
(1.19 at $n=50{,}000$) while DGP~3 (ML score, $\mathrm{SR} = 1.31$) has the
narrowest (0.92), as the upper and lower bounds converge when selection on gains
is weaker.

\begin{table}[htbp]
  \centering
  \small
  \caption{Track B: CATT Estimator and Imbens--Manski CI (nominal 90\%), 1,000 replications}
  \label{tab:trackb}
  \begin{tabular}{lrrrrrr}
    \toprule
    & \multicolumn{2}{c}{CATT estimator} & \multicolumn{2}{c}{IM CI for CATE} \\
    \cmidrule(lr){2-3} \cmidrule(lr){4-5}
    DGP (\textit{true CATE, CATT}) & Bias & RMSE & Coverage & Width \\
    \midrule
    \multicolumn{5}{l}{\textit{Panel A: DGP 1 --- Constant quota (CATE=1.00, CATT=1.70)}} \\
    \quad $n = 500$     & $ 0.015$ & $0.301$ & $0.991$ & $1.207$ \\
    \quad $n = 2{,}000$ & $ 0.002$ & $0.153$ & $1.000$ & $1.192$ \\
    \quad $n = 10{,}000$& $ 0.001$ & $0.065$ & $1.000$ & $1.191$ \\
    \quad $n = 50{,}000$& $-0.001$ & $0.030$ & $1.000$ & $1.190$ \\
    \addlinespace
    \multicolumn{5}{l}{\textit{Panel B: DGP 2 --- Logistic score (CATE=1.00, CATT=1.44)}} \\
    \quad $n = 500$     & $-0.002$ & $0.303$ & $0.930$ & $1.013$ \\
    \quad $n = 2{,}000$ & $ 0.000$ & $0.150$ & $0.997$ & $1.007$ \\
    \quad $n = 10{,}000$& $-0.001$ & $0.068$ & $1.000$ & $1.005$ \\
    \quad $n = 50{,}000$& $ 0.002$ & $0.030$ & $1.000$ & $1.007$ \\
    \addlinespace
    \multicolumn{5}{l}{\textit{Panel C: DGP 3 --- Nonlinear ML score (CATE=1.00, CATT=1.31)}} \\
    \quad $n = 500$     & $-0.009$ & $0.311$ & $0.846$ & $0.924$ \\
    \quad $n = 2{,}000$ & $ 0.005$ & $0.156$ & $0.983$ & $0.924$ \\
    \quad $n = 10{,}000$& $-0.004$ & $0.066$ & $1.000$ & $0.916$ \\
    \quad $n = 50{,}000$& $ 0.000$ & $0.031$ & $1.000$ & $0.917$ \\
    \bottomrule
  \end{tabular}
\end{table}

\paragraph{Track B: assumption-violation robustness (Table~\ref{tab:robust}).}

Table~\ref{tab:robust} reports Track~B performance under DGP-R1 (monotone
selection violated) and DGP-R2 (nonnegative effects violated).  Under both
robustness DGPs, CI coverage collapses to zero: the Imbens--Manski CI fails
to contain the true CATE.  Under DGP-R1 the CI collapses because the upper
bound CATT $= 0.96$ lies strictly below the true CATE $= 1.33$; under DGP-R2
the CI collapses because the lower bound CITT $= 0.42$ lies strictly above the
true CATE $\approx 0$.  These results confirm that the bounds are sharp---they
deliver exactly what is promised under the stated assumptions and nothing more.
In practice, the Selection Ratio upper bound $\mathrm{SR}_{ub} = 1/\bar{e}$
and the sign of $\mathrm{CITT}$ serve as informal diagnostics: if CITT is
implausibly large relative to domain knowledge about average effects, the
nonnegative-effects assumption may warrant scrutiny.

\begin{table}[htbp]
  \centering
  \small
  \caption{Track B: Robustness to Assumption Violations (nominal 90\%, $n = 50{,}000$)}
  \label{tab:robust}
  \begin{tabular}{lrrrrc}
    \toprule
    DGP & True CATE & True CATT & IM CI Coverage & CI Width & Assumption violated \\
    \midrule
    DGP-R1 (hump MTE)      & $1.33$ & $0.96$ & $0.000$ & $0.672$ & Monotone selection \\
    DGP-R2 (neg-tail MTE)  & $0.00$ & $1.40$ & $0.000$ & $0.980$ & Nonneg effects \\
    \bottomrule
  \end{tabular}
\end{table}

\paragraph{Track A: MTE estimation and CATE reconstruction (Table~\ref{tab:tracka}).}

Table~\ref{tab:tracka} reports bias of the finite-differences MTE estimator at
each observed propensity midpoint and RMSE of the integrated CATE estimator
under the geographic excluded-shifter design.

MTE bias at the observed support points is small across all sample sizes: the
largest absolute bias is $0.042$ (at $\bar{p} = 0.275$, $n = 2{,}000$), and
it shrinks to $0.000$--$0.010$ at $n \geq 10{,}000$.  However, the CATE RMSE
plateaus at approximately $0.23$ even as $n$ grows to $200{,}000$, and the
mean estimated CATE converges to $1.22$ rather than the true $1.00$.  This
systematic upward bias reflects \emph{extrapolation error}: the observed market
propensities cover only $[0.20,\,0.55]$, leaving $45\%$ of the unit interval
outside the support.  Linear extrapolation overestimates the MTE in the tails
because the true MTE $\tau(u) = 2(1-u)$ is concave, and the overestimate does
not shrink with $n$.  This finding illustrates a fundamental limitation of the
excluded-shifter approach: reducing sampling variance does not correct
extrapolation bias, which requires either a wider propensity support or
assumptions on the shape of the MTE outside the observed range.

\begin{table}[htbp]
  \centering
  \small
  \caption{Track A: Finite-Differences MTE Estimator and CATE Reconstruction
  (true MTE$(0.275)=1.45$, MTE$(0.450)=1.10$; true CATE $= 1.00$)}
  \label{tab:tracka}
  \begin{tabular}{lrrrr}
    \toprule
    & \multicolumn{2}{c}{MTE bias} & \multicolumn{2}{c}{CATE reconstruction} \\
    \cmidrule(lr){2-3} \cmidrule(lr){4-5}
    $n$ & at $\bar{p}=0.275$ & at $\bar{p}=0.450$ & RMSE & Mean \\
    \midrule
    $2{,}000$   & $0.042$ & $0.006$ & $0.369$ & $1.241$ \\
    $10{,}000$  & $-0.005$ & $-0.005$ & $0.251$ & $1.218$ \\
    $50{,}000$  & $0.008$ & $-0.009$ & $0.227$ & $1.219$ \\
    $200{,}000$ & $0.000$ & $0.003$ & $0.226$ & $1.224$ \\
    \bottomrule
  \end{tabular}
\end{table}

\paragraph{Selection Ratio diagnostic (Table~\ref{tab:sr}).}

Table~\ref{tab:sr} reports Track~B performance under DGP~1 as the treatment
rate $\bar{e}$ varies from $0.10$ to $0.60$.  Imbens--Manski CI coverage is
100\% under all three treatment rates, confirming the sharpness result of
Theorem~\ref{thm:sharp}.  CI width decreases sharply in $\bar{e}$: at $\bar{e}
= 0.10$ (aggressive targeting, SR$_{ub} = 10.0$) the average CI width is 1.72,
while at $\bar{e} = 0.60$ (moderate targeting, SR$_{ub} = 1.67$) the CI width
shrinks to $0.56$, comparable to the standard error band in a well-powered RCT.
This exercise illustrates the managerial interpretation of the Selection Ratio
bound: the observable treatment rate $\bar{e}$ is a sufficient statistic for
the width of the partial identification region, and platforms that target more
selectively produce less informative holdout experiments.

\begin{table}[htbp]
  \centering
  \small
  \caption{Selection Ratio Diagnostic: Varying Treatment Rate (DGP 1, $n = 50{,}000$, nominal 90\%)}
  \label{tab:sr}
  \begin{tabular}{lrrrrr}
    \toprule
    Treatment rate $\bar{e}$ & True SR & SR$_{ub} = 1/\bar{e}$ & IM CI Coverage & CI Width \\
    \midrule
    $0.10$ & $1.90$ & $10.03$ & $1.000$ & $1.720$ \\
    $0.30$ & $1.70$ & $3.34$ & $1.000$ & $1.192$ \\
    $0.60$ & $1.40$ & $1.67$ & $1.000$ & $0.561$ \\
    \bottomrule
  \end{tabular}
\end{table}

% ============================================================
\section{Conclusion}
\label{sec:conclusion}

\subsection{Managerial Implications}
\label{subsec:managerial}

This paper develops identification theory for overlay experiments, in which the
analyst randomizes campaign eligibility while the platform's targeting algorithm
operates freely.  The central practical message is that passive overlay
experiments identify the CATT, not the CATE, and that this gap is systematic
and economically significant in any setting where the platform's algorithm
selects high-responding users.

\emph{Report the right estimand for the decision at hand.}  The CATT answers
the question: ``Did the campaign work for the users the platform chose to
target?''  This is the right question for evaluating campaign quality under the
current targeting strategy and for holding the platform accountable for
delivering the promised audience.  The CATE answers the question: ``What would
happen if we applied this campaign to a larger population?''  This is the right
question for budget-setting and audience-sizing decisions---precisely the
decision problem studied by \citet{waisman2025multicell}.  Advertisers should
explicitly identify which question they are answering before interpreting
experimental results.  Reporting the CATT as if it were the CATE is not merely
imprecise; it is systematically optimistic about scale-up returns.

\emph{Use the Selection Ratio as a scale-up diagnostic.}  Our partial
identification analysis provides a directly computable diagnostic.  The
treatment rate $e(x)$ observed from any overlay experiment immediately bounds the
Selection Ratio: $R(x) \leq 1/e(x)$.  An advertiser observing a 15\% treatment
rate should recognize that the platform may be achieving a selection premium of
up to 6.7x, meaning the CATE for the marginal user could be as low as 15\% of
the observed CATT.  Even if the actual Selection Ratio is far below this upper
bound---which it typically will be in practice---a value of $R(x) = 2$ implies
that doubling the campaign audience will not double revenue, because marginal
users respond at roughly half the rate of those currently targeted.

\emph{Invest in excluded-shifter designs when stakes are high.}  When the
campaign budget is large or the scale-up decision is irreversible, the analyst
should design the overlay experiment to enable point identification of the MTE.
Our analysis shows that geographic variation in market competition, temporal
variation in platform load, or variation in per-market budget caps can serve as
excluded shifters.  Following the spirit of \citet{waisman2025multicell}, an
advertiser can request that the platform vary delivery intensity across geographic
markets or time windows.  The investment in a more informative experimental
design is warranted whenever the partial identification bounds are wide---i.e.,
whenever $e(x)$ is small and the potential for algorithmic cherry-picking is
large.

For practitioners, the key takeaway is that the standard output of an online
advertising experiment---the ATT or CATT from a randomized experiment with
one-sided noncompliance---is an insufficient input for decisions that involve
reaching more consumers or setting a larger budget.  This message, first
articulated clearly in the single-platform setting by \citet{waisman2025multicell},
applies with equal force in the opaque-targeting environment studied here.

\subsection{Limitations and Future Research}
\label{subsec:limitations}

Several limitations of this paper point toward directions for future work.

\emph{Asymptotic theory.}  Section~\ref{subsec:estimation} proposes plug-in
estimators for both tracks, but does not provide a complete asymptotic theory.
Formal rates of convergence, minimax optimality, and the treatment of the
nuisance estimation error in the double/debiased machine learning sense
\citep{chernozhukov2018double} are left for future work.  In particular, for
Track~A the bandwidth selection problem for the derivative estimator
$\hat{\partial}_p\,\mu_1(x,p)$ requires additional analysis; for Track~B the
Imbens--Manski critical value $\hat{c}_n$ has known asymptotic validity under
pointwise asymptotics but its uniform validity requires further study.

\emph{No interference.}  We maintain SUTVA throughout, ruling out interference
between users.  In digital advertising, treated users may affect untreated users
through social influence or through market equilibrium effects such as price
changes and inventory depletion \citep{johari2022experimental}.  Combining the
opaque targeting structure studied here with an interference framework is a
natural direction for future work.

\emph{Binary treatment.}  Our framework treats the treatment as binary.  In
practice, advertising delivery involves multiple exposures, and the dose-response
function is often of primary interest \citep{blake2015consumer}.  Extending the
overlay identification theory to continuous or multi-valued treatments is left
for future work.

\emph{Single platform.}  We study the case in which a single advertiser overlays
a single campaign on a single platform.  The multi-platform and multi-campaign
settings, in which multiple firms simultaneously overlay experiments on the same
platform, introduce additional identification challenges that are not addressed
here.

\emph{Monotone selection.}  Our lower bound relies on monotone selection on
gains, which is an assumption about the platform's optimization rather than a
testable implication of the passive overlay data alone.  Developing tests of
this assumption from overlay data---perhaps using auxiliary information about the
platform's targeting criteria---is an important practical challenge.

% ============================================================
\appendix
\renewcommand{\thesection}{A}
\section*{Appendix: Proofs}
\addcontentsline{toc}{section}{Appendix: Proofs}

\subsection*{Proof of Proposition~\ref{prop:att}}

When $Z_i = 1$, Assumption~\ref{ass:onesided} implies $W_i = D_i$, so
\[
  Y_i = Y_i(D_i) = Y_i(0) + D_i\,\tau_i.
\]
By Assumption~\ref{ass:overlay}, $Z_i \perp (D_i,\, Y_i(0),\, Y_i(1)) \mid X_i$, hence
\[
  E[Y_i \mid Z_i=1, X_i=x] = E[Y_i(0) \mid X_i=x] + E[D_i\,\tau_i \mid X_i=x].
\]
When $Z_i = 0$, Assumption~\ref{ass:onesided} implies $W_i = 0$, so $Y_i =
Y_i(0)$ and
\[
  E[Y_i \mid Z_i=0, X_i=x] = E[Y_i(0) \mid X_i=x].
\]
Subtracting gives $\mathrm{CITT}(x) = E[D_i\,\tau_i \mid X_i=x]$, proving
\eqref{eq:itt}.  Since $D_i$ is binary,
\[
  E[D_i\,\tau_i \mid X_i=x] = E[\tau_i \mid D_i=1, X_i=x]\cdot P(D_i=1 \mid X_i=x)
  = \mathrm{CATT}(x)\cdot e(x).
\]
Dividing by $e(x)$ proves \eqref{eq:catt}. \qed

\subsection*{Proof of Proposition~\ref{prop:representation}}

Fix $(x,p)$ in the support of $(X_i, P_i)$.  Under Assumptions~\ref{ass:onesided}
and~\ref{ass:excluded}, when $Z_i=1$ and $P_i=p$, we have $D_i =
\mathbf{1}\{U_i \leq p\}$, so
\[
  Y_i = Y_i(0) + \mathbf{1}\{U_i \leq p\}\,\tau_i.
\]
By Assumption~\ref{ass:excluded}(5), $Z_i \perp (Y_i(0),\, Y_i(1),\, U_i) \mid
(X_i, S_i)$, and by Assumption~\ref{ass:excluded}(3), $(Y_i(0),\, Y_i(1),\, U_i)
\perp S_i \mid X_i$.  Since $P_i = \pi(X_i, S_i)$ is measurable with respect
to $(X_i, S_i)$, it follows that $(Y_i(0),\, Y_i(1),\, U_i) \perp P_i \mid
X_i$.  Therefore,
\begin{align*}
  \mu_1(x,p)
  &= E[Y_i(0) \mid X_i=x] + E[\mathbf{1}\{U_i\leq p\}\,\tau_i \mid X_i=x] \\
  &= \mu_0(x) + \int_0^p E[\tau_i \mid X_i=x,\, U_i=u]\,du
   = \mu_0(x) + \int_0^p \mathrm{MTE}(x,u)\,du,
\end{align*}
where the last step uses Assumption~\ref{ass:excluded}(2). \qed

\subsection*{Proof of Theorem~\ref{thm:pointid}}

Differentiating both sides of \eqref{eq:representation} with respect to $p$
gives $\partial_p\,\mu_1(x,p) = \mathrm{MTE}(x,p)$, proving part 1.  Under full
support, $\mathrm{CATE}(x) = E[\tau_i \mid X_i=x] = \int_0^1
E[\tau_i \mid X_i=x,\, U_i=u]\,du = \int_0^1 \mathrm{MTE}(x,u)\,du$ by
Assumption~\ref{ass:excluded}(2), proving part 2.  Part 3 follows by the law of
iterated expectations. \qed

\subsection*{Proof of Lemma~\ref{lem:overlay}}

By Proposition~\ref{prop:att} and Assumption~\ref{ass:passive}, $D_i =
\mathbf{1}\{e(X_i) \geq U_i\}$, so
\[
  \mathrm{CITT}(x) = E[D_i\,\tau_i \mid X_i=x]
  = \int_0^{e(x)} E[\tau_i \mid X_i=x,\, U_i=u]\,du
  = \int_0^{e(x)} \mathrm{MTE}(x,u)\,du,
\]
proving \eqref{eq:citt_rep}.  Equation~\eqref{eq:cate_rep} follows by
integrating the MTE over all of $[0,1]$ using Assumption~\ref{ass:passive}. \qed

\subsection*{Proof of Theorem~\ref{thm:sharp}}

By Lemma~\ref{lem:overlay},
$\mathrm{CITT}(x) = \int_0^{e(x)}\mathrm{MTE}(x,u)\,du$ and
$\mathrm{CATE}(x) = \int_0^1 \mathrm{MTE}(x,u)\,du$.

\textit{Upper bound.}  By Assumption~\ref{ass:monotone}, the average MTE over
$[e(x),1]$ is no greater than the average over $[0,e(x)]$:
\[
  \mathrm{CATU}(x) = \frac{1}{1-e(x)}\int_{e(x)}^1\!\mathrm{MTE}(x,u)\,du
  \;\leq\; \frac{1}{e(x)}\int_0^{e(x)}\!\mathrm{MTE}(x,u)\,du = \mathrm{CATT}(x).
\]
Using $\mathrm{CATE}(x) = e(x)\,\mathrm{CATT}(x) + (1-e(x))\,\mathrm{CATU}(x)$
and $\mathrm{CATU}(x) \leq \mathrm{CATT}(x)$ yields $\mathrm{CATE}(x) \leq
\mathrm{CATT}(x)$.

\textit{Lower bound.}  By Assumption~\ref{ass:nonneg},
$\int_{e(x)}^1\mathrm{MTE}(x,u)\,du \geq 0$, so
$\mathrm{CATE}(x) = \mathrm{CITT}(x) + \int_{e(x)}^1\mathrm{MTE}(x,u)\,du
\geq \mathrm{CITT}(x)$.

\textit{Sharpness.}  Write $p := e(x)$ and $I := \mathrm{CITT}(x)$.  The
schedule $m^L(u) = (I/p)\,\mathbf{1}\{u \leq p\}$ is weakly decreasing and
nonnegative, generates $\mathrm{CITT}(x) = I$, and yields $\mathrm{CATE}(x) = I =
\mathrm{CITT}(x)$.  The schedule $m^U(u) \equiv I/p$ is constant, generates
$\mathrm{CITT}(x) = I$, and yields $\mathrm{CATE}(x) = I/p = \mathrm{CATT}(x)$.
Convex combinations $m^\lambda = \lambda\,m^U + (1-\lambda)\,m^L$ are weakly
decreasing and nonnegative, generate $\mathrm{CITT}(x) = I$, and yield
$\mathrm{CATE}(x) = \lambda\,\mathrm{CATT}(x) + (1-\lambda)\,\mathrm{CITT}(x)$,
attaining every value in $[\mathrm{CITT}(x),\, \mathrm{CATT}(x)]$. \qed

\subsection*{Proof of Corollary~\ref{cor:ratio}}

Since $\mathrm{CATE}(x) \in [\mathrm{CITT}(x),\, \mathrm{CATT}(x)]$ and
$\mathrm{CITT}(x) = e(x)\,\mathrm{CATT}(x)$:
\[
  R(x) = \frac{\mathrm{CATT}(x)}{\mathrm{CATE}(x)}
  \;\in\; \left[\frac{\mathrm{CATT}(x)}{\mathrm{CATT}(x)},\;
               \frac{\mathrm{CATT}(x)}{e(x)\,\mathrm{CATT}(x)}\right]
  = \left[1,\;\frac{1}{e(x)}\right]. \qed
\]

% ============================================================
\bibliographystyle{apalike}
\bibliography{refs}

\end{document}
